### 2011-07-18 Paper/Paper.tex
Small paper update. Hmm working better, performance rendering broken. Probabilities sum more to one

\begin{itemize}
\item Extract melody
\item Extract scorefeatures from melody
\item lookup notes in deviation, ignore missing notes
\item Extract expressive and non-expressive melody and extract expression features
\item Perform notes other than melody notes the same as the nearest melody note
\end{itemize}
\subsection{Corpus and Representation}
We were lucky to find and receive permission to use the CrestMusePEDB \ref{crestmuse} corpus, which is a corpus that contains expressive performances of Western classical music by famous pianists. The corpus contains about

@@

\subsection{Dealing with polyphony}
\begin{itemize}
\item Use only melody
\end{itemize}
\subsection{Discretization}

\begin{itemize}
\item Normalize every feature
\item Discretization: int($\phi * d$) where d is the discretization parameter (the higher, the smaller the bins)
\end{itemize}

Discretization of expression is a delicate subject, we want to capture small changes in dynamics and tempo precisely, but outliers may fall in large bins. A sigmoid function is very useful for this purpose.

All expression parameters are ratios: their values vary around 1.0. To get a linear scale we use the logarithmic ratio. The tempo ratio is defined as: $\log(\frac{\texttt{performancetempo}}{\texttt{scoretempo}})$. To get the desired properties of discretization we use a sigmoid function. $D(p) = d * \frac{1}{1+e^{-p}}$ where $D(p)$ is the discretization of $p$, $e$ is the expression parameter value and $p$ is the discretization parameter.
\subsection{Performance rendering}
\begin{itemize}
\item Extract melody
\item Extract scorefeatures from melody
\item lookup notes in deviation, ignore missing notes
\item Extract expressive and non-expressive melody and extract expression features
\item Perform notes other than melody notes the same as the nearest melody note
\end{itemize}

>>>>

\begin{itemize}
\item Extract melody
\item Extract scorefeatures from melody
\item lookup notes in deviation, ignore missing notes
\item Extract expressive and non-expressive melody and extract expression features
\item Perform notes other than melody notes the same as the nearest melody note
\end{itemize}
\subsection{Corpus and Representation}
We were lucky to find and receive permission to use the CrestMusePEDB \ref{crestmuse} corpus, which is a corpus that contains expressive performances of Western classical music by famous pianists. The music includes works by Bach, Beethoven and Chopin.

@@

\subsection{Dealing with polyphony}
\begin{itemize}
\item Use only melody
\end{itemize}
\subsection{Discretization}
To calculate probabilities, we must discretize the feature and parameter vectors.

\paragraph*{Expression} Discretization of expression parameters is a delicate subject, we want to capture small changes in dynamics and tempo precisely, but outliers may fall in large bins. A sigmoid function is very useful for this purpose. The expression parameters are all logarithmic ratios so they theoretically vary from $-\infty$ to $\infty$. Therefore we first normalize the parameters by dividing through the mizimum absolute value found in the corpus. Discretization of a normalized expression parameter $p$ into $d$ bins is now done as follows:

\begin{equation}
D(p) = \texttt{floor}\left(\frac{d}{1+e^{-sp}}\right)
\end{equation}

Where $D(p)$ is the discretization of $p$, $s$ is a special sensitivity parameter indicating how small the changes in tempo that the discretization captures can be; a larger $s$ means a more sensitive discretization. Undiscretization is the reverse operation:

\begin{equation}
D^{-1}(p) = s^{-1} d^{-1}(-\log(p^{-1}) - 1)
\end{equation}

\paragraph*{Features}

To discretize the features, we simply normalize every feature dividing through the maximum absolute value of that feature found in the corpus. After normalization we multiply the feature by a discretization parameter that determines the number of bins and take the floor.

\begin{equation}
D(f) = \texttt{floor}(f*d)
\end{equation}

Where $f$ is the normalized feature value.

\subsection{Performance rendering}
\begin{itemize}
\item Extract melody
\item Extract scorefeatures from melody
\item lookup notes in deviation, ignore missing notes
\item Extract expressive and non-expressive melody and extract expression features
\item Perform notes other than melody notes the same as the nearest melody note
\end{itemize}
